---
title: "Asian Swamp Eel Diet Data "
author: "Brandon Güell & Alyssa Herrera"
date: "12/7/2023"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---
PDF Knit settings
```{r global_options}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

#Load Packages/Data
```{r}
library(tidyr)
library(readxl)
library(dplyr)
library(ggplot2)
library(scales)
library(lme4)
library(car)
library(lmerTest)
library(emmeans)
library(EnvStats)

eeldiet <- read.csv("Asian Swamp Eel Dissection.csv")
```

# Summary Statistics
```{r}
# Adding Size Classes
eeldiet = eeldiet %>%
  mutate(Size_class = case_when(TL_mm < 300 ~ 'A',
                                between(TL_mm, 300, 450) ~ 'B',
                                between(TL_mm, 450, 600) ~ 'C',
                                TL_mm > 600 ~ 'D'))
```

##Sizes by Region
```{r}
#Total sample size from each region
eel_Regions = eeldiet %>%
  filter(Region != "NA") %>%
  group_by(Region) %>%
  summarize(
    Without_Contents = sum(NOPREY == 1, na.rm = TRUE),
    With_Contents = sum(is.na(NOPREY) | NOPREY == ""),
    Total_Eels = n())

#Swamp eel size summary statistics by region
eel_Regions = eeldiet %>%
  group_by(Region) %>%
  summarise(mean_size = mean(TL_mm, na.rm=T), SE= sd(TL_mm,na.rm=T)/sqrt(length(TL_mm)), SD = sd(TL_mm, na.rm=T), min= min(TL_mm, na.rm=T), max= max(TL_mm, na.rm=T), sample_size_unique=n_distinct(TL_mm, na.rm=T), sample_size=n())
eel_Regions
```

Eel measurements
```{r}
#Eel Sizes per region
eel_size = eeldiet %>%
  summarise(mean_size = mean(TL_mm, na.rm=T), SE= sd(TL_mm,na.rm=T)/sqrt(length(TL_mm)), SD = sd(TL_mm, na.rm=T), min= min(TL_mm, na.rm=T), max= max(TL_mm, na.rm=T), sample_size_unique=n_distinct(TL_mm, na.rm=T), sample_size=n())
eel_size

eel_size = eeldiet %>%
  group_by(Region) %>%
  summarise(mean_size = mean(TL_mm, na.rm=T), SE= sd(TL_mm,na.rm=T)/sqrt(length(TL_mm)), SD = sd(TL_mm, na.rm=T), min= min(TL_mm, na.rm=T), max= max(TL_mm, na.rm=T), sample_size_unique=n_distinct(TL_mm, na.rm=T), sample_size=n())
eel_size

eel_size = eeldiet %>%
  group_by(Size_class) %>%
  summarise(mean_size = mean(TL_mm, na.rm=T), SE= sd(TL_mm,na.rm=T)/sqrt(length(TL_mm)), SD = sd(TL_mm, na.rm=T), min= min(TL_mm, na.rm=T), max= max(TL_mm, na.rm=T), sample_size_unique=n_distinct(TL_mm, na.rm=T), sample_size=n())
eel_size
```

##Cannibalism 
```{r}
region_summary <- eeldiet %>%
  filter(Region != "NA") %>%
  group_by(Invasion_Status) %>%
  summarise(
    total = n(),
    cannibal_count = sum(MONALB == 1),
    prop_cannibal = cannibal_count / total)

# Calculate mean years since invasion for each region
eeldiet$Years_Since_Invasion <- as.numeric(eeldiet$Years_Since_Invasion)
region_years <- eeldiet %>%
  group_by(Region) %>%
  summarise(years = round(mean(Years_Since_Invasion, na.rm = TRUE), 0))

# Summarize with standard error
region_summary <- eeldiet %>%
  filter(Region != "NA") %>%
  group_by(Region) %>%
  summarise(
    total = n(),
    cannibal_count = sum(MONALB == 1),
    prop_cannibal = cannibal_count / total,
    se = sqrt((prop_cannibal * (1 - prop_cannibal)) / total))

region_summary <- region_summary %>%
  left_join(region_years, by = "Region")
max_y <- max(region_summary$prop_cannibal + region_summary$se, na.rm = TRUE)

# Plot with error bars
Cannibalism_Proportions <- ggplot(region_summary, aes(x =  reorder(Region, -years), y = prop_cannibal)) +
  geom_bar(stat = "identity", fill = "#0072B2") +
  # Avg years since invasion
  geom_text(aes(label = paste0(years, " years"), y = max_y + 0.02), size = 4) +
  labs(
    x = "Region",
    y = "Proportion of eels exhibiting cannibalism"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black", size = 0.3),
    axis.title.x = element_text(size = 12, margin = margin(t = 8)),  
    axis.title.y = element_text(size = 12, margin = margin(r = 10)),  
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1),  
    axis.text.y = element_text(size = 10)
  )

Cannibalism_Proportions
ggsave("Cannibalism_Proportions.eps", Cannibalism_Proportions, width = 6, height = 4, dpi = 800)

# Create contingency table
table_region_cannibal <- table(eeldiet$Region, eeldiet$MONALB)

# Perform Chi-squared test
chisq.test(table_region_cannibal)

# Create contingency table
table_region_cannibal <- table(eeldiet$Invasion_Status, eeldiet$MONALB)

# Perform Chi-squared test
chisq.test(table_region_cannibal)
```

#Frequency of occurence
```{r}
#Removing eels without gut contents from data
eeldiet = eeldiet[-(which(eeldiet$NOPREY %in% 1)),]

#Creating Prey categories
eeldiet = eeldiet %>%
  mutate(Fish = CICSPP+CICURO+ELAEVE+ENNGLO+FUNCHR+GAMHOL+HETFOR+JORFLO+LUCGOO+MONALB+UNIFIS+ HEMLET) %>%
  mutate(Shrimp = PALPAL) %>%
  mutate(Crayfish = PROFAL) %>%
  mutate(Odonata= BRAGRA+CELSPP+COENAG+ERYSIM+ERYSPP+LIBSPP+MACBAL+ODONAT+PACLON+ANAJUN+CORING) %>%
  mutate(Hemiptera = BELSPP+PELBAL+PELFEM+PELSPP) %>%
  mutate(Coleoptera = COLEOL+DYTCEL+DYTSPP+HYDSPP+NEOUNI) %>%
  mutate(Gastropoda = APHPAC+HAISPP+ PLASPP) %>%
  mutate(Diptera = STRATI+CYBSPP+ DOLICH+TABANI) %>%
  mutate(Unknown_Insects = UNIINV) %>%
  mutate(Amphipoda = AMPHOP) %>%
  mutate(Miscellaneous = DETRIT+ EGG+ RANATP+ UNIDEN+ PHIFLO)
eeldiet

### Grouping master data table for occurrence summaries Manipulate Data tidyr
eeldiet_occurences = eeldiet %>%
  tidyr::gather(key = "Prey", value = "Count", Fish:Miscellaneous, na.rm = FALSE, convert = FALSE, factor_key = FALSE) %>%
  arrange(Eel_count) %>%
  mutate(Presence = case_when(Count > 0 ~ 1, Count == 0 ~ 0))
eeldiet_occurences
```

### Percent Occurrence tables
```{r}
#Occurrence by PREY
diet_occurences_summary_Prey <- eeldiet_occurences %>%
  group_by(Prey) %>%
  summarise(
    occurrence = sum(Presence, na.rm = TRUE),
    sample_size = n(),
    frequency_occurrence = occurrence / sample_size,
    se_frequency = sqrt((frequency_occurrence * (1 - frequency_occurrence)) / sample_size),
    percent_occurrence = frequency_occurrence * 100,
    se_percent = se_frequency * 100) %>%
  arrange(Prey)
diet_occurences_summary_Prey

#Occurrence by REGION
diet_occurences_summary_Region = eeldiet_occurences %>%
  group_by(Prey, Region) %>%
  summarise(N = sum(Count, na.rm=T),occurrence= sum(Presence, na.rm=T), sample_size=n(), percent_occurrence = (occurrence/(sample_size=n())*100), frequency_occurrence = (occurrence/(sample_size=n()))) %>%
  arrange(Region)
diet_occurences_summary_Region

#Occurrence by SIZE CLASS
diet_occurences_summary_size = eeldiet_occurences %>%
  group_by(Prey, Size_class) %>%
  summarise(N = sum(Count, na.rm=T), occurrence= sum(Presence, na.rm=T), sample_size=n(), percent_occurrence = (occurrence/(sample_size=n())*100), frequency_occurrence = (occurrence/(sample_size=n()))) %>%
  arrange(Size_class)
diet_occurences_summary_size

#Occurrence by REGION & SIZE CLASS
diet_occurences_summary_Region_Size = eeldiet_occurences %>%
  group_by(Prey, Size_class, Region) %>%
  summarise(occurrence= sum(Presence, na.rm=T), sample_size=n(), percent_occurrence = (occurrence/(sample_size=n())*100),frequency_occurrence = (occurrence/(sample_size=n()))) %>%
  arrange(Size_class)
diet_occurences_summary_Region_Size
```

###Summaries of filtered occurrence tables 
```{r}
#Descriptive Statistics of Occurrences
eeldiet_occurences_summary = eeldiet_occurences %>%
  group_by(Prey) %>%
  summarise(mean = mean(Count, na.rm=T), SE= sd(Count,na.rm=T)/sqrt(length(Count)), SD = sd(Count, na.rm=T), min= min(Count, na.rm=T), max= max(Count, na.rm=T), sum= sum(Count, na.rm=T), sample_size_unique=n_distinct(Count, na.rm=T), sample_size=n())
eeldiet_occurences_summary

eeldiet_occurences_summary = eeldiet_occurences %>%
  group_by(Region, Size_class) %>%
  summarise(mean = mean(Count, na.rm=T), SE= sd(Count,na.rm=T)/sqrt(length(Count)), SD = sd(Count, na.rm=T), min= min(Count, na.rm=T), max= max(Count, na.rm=T), sum= sum(Count, na.rm=T), sample_size_unique=n_distinct(Count, na.rm=T), sample_size=n())
eeldiet_occurences_summary

eeldiet_occurences_summary = eeldiet_occurences %>%
  group_by(Region) %>%
  summarise(mean = mean(Count, na.rm=T), SE= sd(Count,na.rm=T)/sqrt(length(Count)), SD = sd(Count, na.rm=T), min= min(Count, na.rm=T), max= max(Count, na.rm=T), sum= sum(Count, na.rm=T), sample_size_unique=n_distinct(Count, na.rm=T), sample_size=n())
eeldiet_occurences_summary

eeldiet_occurences_summary = eeldiet_occurences %>%
  group_by(Size_class, Prey) %>%
  summarise(mean = mean(Count, na.rm=T), SE= sd(Count,na.rm=T)/sqrt(length(Count)), SD = sd(Count, na.rm=T), min= min(Count, na.rm=T), max= max(Count, na.rm=T), sum= sum(Count, na.rm=T), sample_size_unique=n_distinct(Count, na.rm=T), sample_size=n())
eeldiet_occurences_summary
```

#Biomass of Prey
```{r}
#Replacing NA values with zeroes in order to add together biomass values
eeldiet[,64:113][is.na(eeldiet[, 64:113])] <- 0

#Adding together dry weight biomass of prey and organizing them into categories
eeldiet_biomass = eeldiet %>%
  mutate(Fish = CICSPP_mass+CICURO_mass+ELAEVE_mass+ENNGLO_mass+FUNCHR_mass+GAMHOL_mass+HETFOR_mass+JORFLO_mass+LUCGOO_mass+UNIFIS_mass+MONALB_mass+ HEMLET_mass) %>%
  mutate(Shrimp = PALPAL_mass) %>%
  mutate(Crayfish = PROFAL_mass) %>%
  mutate(Odonata= BRAGRA_mass+CELSPP_mass+COENAG_mass+ERYSIM_mass+ERYSPP_mass+LIBSPP_mass+ MACBAL_mass+ODONAT_mass+PACLON_mass+ ANAJUN_mass+CORING_mass) %>%
  mutate(Hemiptera = BELSPP_mass+PELBAL_mass+PELFEM_mass+PELSPP_mass) %>%
  mutate(Coleoptera = COLEOL_mass +DYTCEL_mass+DYTSPP_mass+HYDSPP_mass+NEOUNI_mass) %>%
  mutate(Gastropoda = APHPAC_mass+HAISPP_mass+ PLASPP_mass) %>%
  mutate(Diptera = STRATI_mass+CYBSPP_mass+DOLICH_mass+TABANI_mass) %>%
  mutate(Unknown_Insects = UNIINV_mass) %>%
  mutate(Amphipoda = AMPHOP_mass) %>%
  mutate(Miscellaneous = DETRIT_mass+ EGG_mass+ RANATP_mass+ UNIDEN_mass+ PHIFLO_mass) %>%
  mutate(total_biomass= AMPHOP_mass+ ANAJUN_mass+ APHPAC_mass+	BELSPP_mass	+BRAGRA_mass+CELSPP_mass	+CICSPP_mass+	CICURO_mass+	COENAG_mass+CORING_mass+ CYBSPP_mass+	DETRIT_mass+ DOLICH_mass+	DYTCEL_mass+	DYTSPP_mass+	EGG_mass+	ELAEVE_mass+	ENNGLO_mass+	ERYSIM_mass+	ERYSPP_mass+	FUNCHR_mass+	GAMHOL_mass+	HAISPP_mass+ HEMLET_mass+	HETFOR_mass+ JORFLO_mass+	HYDSPP_mass+	LIBSPP_mass+	LUCGOO_mass+	MONALB_mass+	NEOUNI_mass+	ODONAT_mass+	PACLON_mass+	PALPAL_mass+	PELBAL_mass+	PELFEM_mass+	PELSPP_mass+ PHIFLO_mass+	PLASPP_mass+	PROFAL_mass+	RANATP_mass+	STRATI_mass+ TABANI_mass+	UNIDEN_mass+	UNIFIS_mass+	UNIINV_mass)
eeldiet_biomass

#Organizes data so each eel has a row reflecting a different prey category
eeldiet_biomass = eeldiet_biomass %>%
  tidyr::gather(key = "Prey", value = "Biomass", Fish:Miscellaneous, na.rm = FALSE, convert = FALSE, factor_key = FALSE) %>%
  arrange(Eel_count)
eeldiet_biomass

#Finding percent biomass for each consumed category per individual eel
eeldiet_biomass = eeldiet_biomass %>%
  group_by(Prey) %>%
  mutate(prop_biomass= (Biomass/total_biomass)*100)
eeldiet_biomass
```

###Prey biomass summaries
```{r}
#Percent Biomass Grouping by Region and Size Class

#All eels
eeldiet_biomass_summary <- eeldiet_biomass %>%
  group_by(Prey) %>%
  summarise(percent_biomass = (sum(Biomass, na.rm = TRUE) / sum(total_biomass, na.rm = TRUE)) * 100,
    SE= sd((prop_biomass),na.rm=T)/ sqrt(n()),
    sample_size = n()) %>%
  arrange(desc(percent_biomass))
eeldiet_biomass_summary

#By Region
eeldiet_biomass_region <- eeldiet_biomass %>%
  group_by(Prey, Region) %>%
  filter(Region != "NA")%>%
  summarise(
    percent_biomass = (sum(Biomass, na.rm = TRUE) / sum(total_biomass, na.rm = TRUE)) * 100,
    SE= sd(prop_biomass,na.rm=T)/ sqrt(n()),
    sample_size = n()) %>%
  arrange(Region, desc(percent_biomass))

#By Size Class
eeldiet_biomass_summary_size <- eeldiet_biomass %>%
  filter(Region != "NA") %>%
  group_by(Prey, Size_class) %>%
  summarise(
    percent_biomass = (sum(Biomass, na.rm = TRUE) / sum(total_biomass, na.rm = TRUE)) * 100,
    SE = sd(prop_biomass, na.rm = TRUE) / sqrt(n()),
    sample_size = n()) %>%
  arrange(Size_class, desc(percent_biomass))

#By Region and Size Class
eeldiet_biomass_summary_size_region <- eeldiet_biomass %>%
  group_by(Prey, Size_class, Region) %>%
  filter(Region != "NA") %>%
  summarise(
    percent_biomass = round((sum(Biomass, na.rm = TRUE) / sum(total_biomass, na.rm = TRUE)) * 100, 2),
    SE= sd(prop_biomass,na.rm=T)/ sqrt(n()),
    sample_size = n()) %>%
  arrange(Region, Size_class, desc(percent_biomass))
```
##Prey Specific Abundance
```{r}
#averaged across eels to achieve prey importance equaling to 100%
spec.abundance = eeldiet_biomass %>%
  group_by(Prey) %>%
  filter(prop_biomass > 0)%>%
 summarise(specific_abundance = mean(prop_biomass), sample_size=n())
spec.abundance

SpecAbun_Region = eeldiet_biomass %>%
  group_by(Prey, Region) %>%
  filter(Region != "NA", prop_biomass > 0) %>%
  summarise(specific_abundance = mean(prop_biomass), sample_size=n())
SpecAbun_Region

SpecAbun_Size = eeldiet_biomass %>%
  group_by(Prey, Size_class) %>%
  filter(prop_biomass > 0) %>%
  summarise(specific_abundance = mean(prop_biomass), sample_size=n())
SpecAbun_Size

SpecAbun_Region_Size = eeldiet_biomass %>%
  group_by(Prey, Region, Size_class) %>%
   filter(Region != "NA", prop_biomass > 0) %>%
  summarise(specific_abundance = mean(prop_biomass), sample_size=n())
SpecAbun_Region_Size
```

Arranging occurrence data tables for Prey Importance calculations
```{r}
#Merging specific abundance and percent occurrence into the same data frames
##Filtering occurrence tables to take out 0 values
diet_occurences_summary_Prey = diet_occurences_summary_Prey %>%
  group_by(Prey) %>%
  filter(percent_occurrence > 0) %>%
  arrange(Prey)
diet_occurences_summary_Prey

diet_occurences_summary_Region = diet_occurences_summary_Region %>%
  group_by(Prey, Region) %>%
  filter(percent_occurrence > 0) %>%
  arrange(Prey)
diet_occurences_summary_Region

diet_occurences_summary_size = diet_occurences_summary_size %>%
  group_by(Prey, Size_class) %>%
  filter(percent_occurrence > 0) %>%
  arrange(Prey)
diet_occurences_summary_size

diet_occurences_summary_Region_Size = diet_occurences_summary_Region_Size %>%
  group_by(Prey, Size_class, Region) %>%
  filter(percent_occurrence > 0) %>%
  arrange(Prey)
diet_occurences_summary_Region_Size

##Merging occurrence and specific abundance tables
PI = right_join(diet_occurences_summary_Prey, spec.abundance, by = c('Prey'))

PI_Region = right_join(diet_occurences_summary_Region, SpecAbun_Region, by = c('Prey', 'Region'))

PI_Size = right_join(diet_occurences_summary_size, SpecAbun_Size, by = c('Prey', 'Size_class'))

PI_Region_Size = right_join(diet_occurences_summary_Region_Size, SpecAbun_Region_Size, by = c('Prey', 'Size_class', 'Region'))
```


#Prey Importance
```{r}
#Just by prey
PI= PI %>%
  mutate(prey_importance = ((specific_abundance)*(frequency_occurrence)))%>%
  filter(Prey != "Crustaceans")
PI = right_join(eeldiet_biomass_summary, PI , by = c('Prey'))%>%
  dplyr::select(Prey, occurrence, percent_occurrence, percent_biomass, SE,specific_abundance, prey_importance)%>%
   mutate(
    percent_occurrence = round(percent_occurrence, 1),
    SE = round(SE, 2),
    percent_biomass = round(percent_biomass, 8),
    specific_abundance = round(specific_abundance, 1),
    prey_importance = round(prey_importance, 1)) %>%
  arrange(desc(prey_importance))

#Region
PI_Region = PI_Region %>%
  mutate(prey_importance = ((specific_abundance)*(frequency_occurrence)))%>%
  filter(Prey != "Crustaceans", Region != "NA")
PI_Region= right_join(eeldiet_biomass_region, PI_Region , by = c('Prey', 'Region'))%>%
  dplyr::select(Region, Prey, N, occurrence, percent_occurrence, percent_biomass, SE,specific_abundance, prey_importance) %>%
   mutate(
    percent_occurrence = round(percent_occurrence, 1),
    SE = round(SE, 4),
    percent_biomass = round(percent_biomass, 4),
    specific_abundance = round(specific_abundance, 1),
    prey_importance = round(prey_importance, 1)) %>%
  arrange(Region, desc(prey_importance))

#Size
PI_Size = PI_Size %>%
  mutate(prey_importance = ((specific_abundance)*(frequency_occurrence)))%>%
  filter(Prey != "Crustaceans")
PI_Size = right_join(eeldiet_biomass_summary_size, PI_Size , by = c('Prey', 'Size_class'))%>%
  dplyr::select(Size_class, Prey, N, occurrence, percent_occurrence, percent_biomass, SE,specific_abundance, prey_importance)%>%
  mutate(
    percent_occurrence = round(percent_occurrence, 1),
    SE = round(SE, 4),
    percent_biomass = round(percent_biomass, 4),
    specific_abundance = round(specific_abundance, 1),
    prey_importance = round(prey_importance, 1),) %>%
  arrange(Size_class, desc(prey_importance))

#Region and Size
PI_Region_Size = PI_Region_Size %>%
  mutate(prey_importance = ((specific_abundance)*(frequency_occurrence)))%>%
  filter(Prey != "Crustaceans", Region != "NA")
PI_Region_Size = right_join(eeldiet_biomass_summary_size_region, PI_Region_Size , by = c('Prey', 'Size_class', 'Region'))%>%
  dplyr::select(Prey, Region,Size_class, sample_size.y, occurrence, percent_occurrence, percent_biomass, SE,specific_abundance, prey_importance) %>%
   mutate(
    percent_occurrence = round(percent_occurrence, 2),
    SE = round(SE, 2),
    prey_importance = round(prey_importance, 1)) %>%
  arrange(Region, Size_class, desc(prey_importance))
PI_Region_Size
```

###Stacked PI Plot: Region+Size
```{r}
sample_sizes <- data.frame(
  Region = c("PHD","PHD","PHD","PHD", "TSL","TSL","TSL","TSL", "WCA 3B","WCA 3B","WCA 3B","WCA 3B","SRS", "SRS","SRS","SRS", "WCA 3A","WCA 3A","WCA 3A","WCA 3A"),
  Size_class = c("A", "B", "C", "D"), 
  sample_size = c(50,86,34,32,22,59,47,47,6,21,28,4,11,19,12,16,26,97,27,17))

PI_Region_Size$Prey <- factor(PI_Region_Size$Prey,
  levels = c("Miscellaneous", "Unknown_Insects",  
             "Coleoptera", "Diptera", "Gastropoda","Amphipoda", "Shrimp", 
             "Hemiptera", "Fish", "Crayfish", "Odonata"))

PI_Region_Size$Region <- factor(
  PI_Region_Size$Region,
  levels = c("PHD", "TSL", "WCA 3B", "SRS", "WCA 3A"))

# Merge sample sizes with main data for correct mapping
PI_Region_Size <- merge(PI_Region_Size, sample_sizes, by = c("Region", "Size_class")) %>% mutate(Size_class_label = dplyr::recode(as.character(Size_class),
                                         "A" = "<300",
                                         "B" = "300-450",
                                         "C" = "450-600",
                                         "D" = ">600"))

# Create the plot with sample sizes above columns
PI_Region_Size_graph <- ggplot(PI_Region_Size, aes(x = Size_class_label, y = prey_importance, fill = Prey)) +
  geom_bar(stat = "identity", position = "fill") +
  scale_y_continuous(
  labels = function(x) x * 100,
  breaks = seq(0, 1, 0.2))+
  scale_x_discrete(limits = c("<300", "300-450", "450-600", ">600")) +
  scale_fill_manual(name = "Prey type",
                    values = c("Crayfish" = "#B22222", 
                               "Fish" = "#004080", 
                               "Gastropoda" = "#006400", 
                               "Hemiptera" = "#808000", 
                               "Odonata" = "#654321",
                               "Shrimp" = "#FC8EAC",
                               "Unknown_Insects" = "#9370DB",
                               "Miscellaneous" = "#FF8C00",
                               "Diptera" = "#00BFFF",
                               "Coleoptera" = "#32CD32",
                               "Amphipoda" = "#FF4500"),
  labels = c(
    "Crayfish" = "Crayfish",
    "Fish" = "Fish",
    "Gastropoda" = "Snails",
    "Hemiptera" = "Aquatic bugs",
    "Odonata" = "Dragonfly naiads",
    "Shrimp" = "Grass shrimp",
    "Unknown_Insects" = "Unknown insects",
    "Miscellaneous" = "Miscellaneous",
    "Diptera" = "Fly larvae",
    "Coleoptera" = "Beetles",
    "Amphipoda" = "Amphipods")) +
  labs(y = "Prey importance", x = "Size class (mm)") +
  theme_minimal() +
  facet_wrap(
  ~ Region,
  nrow = 1,
  labeller = labeller(
    Region = c(
      "PHD" = "PHD\n(8 years)",
      "TSL" = "TSL\n(8 years)",
      "WCA 3B" = "WCA 3B\n(4 years)",
      "SRS" = "SRS\n(3 years)",
      "WCA 3A" = "WCA 3A\n(2 years)"))) + 
  theme(
    axis.title.x = element_text(size = 10, margin = margin(t = 3)),  
    axis.title.y = element_text(size = 10),  
    axis.text.x = element_text(size = 9, angle = 45, hjust = 1, margin = margin(t = -7)),  
    axis.text.y = element_text(size = 9),  
    legend.title = element_text(size = 9, hjust = 0.5, vjust = 0.5),  
    legend.text = element_text(size = 8),  
    legend.position = "right",  
    legend.justification = "left", 
     legend.key.size = unit(0.3, "cm"),
    panel.spacing = unit(1, "lines"),
    strip.text = element_text(size = 9, margin = margin(t = 5, b = 0)), strip.background = element_blank(),
  panel.grid = element_blank())+
  geom_text(data = PI_Region_Size,
          aes(x = Size_class_label, y = 1.03, label = sample_size),
          inherit.aes = FALSE,size = 3.00,fontface = "plain")
PI_Region_Size_graph
ggsave("Stacked_Plot_Region_Size__.eps", PI_Region_Size_graph, width = 6, height = 4, dpi = 800)
```



